Supplementary Information

### 2021-01-12 doc/manuscript/MEE_manuscript.Rmd
Update MEE_manuscript.Rmd
note: no changes to climate sensitivity results for RW-only models
Update MEE_manuscript.Rmd
#108

```{r , eval=FALSE, echo=FALSE}
## Tallies for the  paragraph below (Jan6)

@@

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Jan6)
n_spst_DBH_analyzed= 43 # n species with DBH analyzed: 43 (45 - 2: 2 Hansley)
n_spst_RW_DBH_sig=35 #  species with sig first-order linear DBH term
n_spst_RW_DBH_2nd_order=27
n_spst_RW_DBH_2nd_order_neg=22
n_spst_BAI_DBH_best_model=42 #exception: ACRU at HF and 
n_spst_BAI_DBH_best_model_neg=40 #exceptions: PIPO at LT (reconstructed DBH down to only 15cm) and PILO at CB (short DBH range on old trees), both neg but not significant
n_spst_BAI_DBH_best_model_2nd=41
n_spst_BAI_DBH_best_model_2nd_neg=40 # exception: PILO at CB
n_spst_dAGB_DBH_best_model=42 # exception: PILO at CB
```

@@

**Trends in both $BAI$ and $\Delta AGB$ were far more consistent across sites and species, most commonly increasing to a peak at intermediate $DBH$ and then declining (Fig. `r size`).**
Best models for $BAI$ included $DBH$ and $DBH^2$ for `r n_spst_BAI_DBH_best_model` of `r n_spst_DBH_analyzed` species (exception: *Acer rubrum* at HF), with a positive coefficient for $DBH$ in `r n_spst_BAI_DBH_best_model_neg` (exceptions: non-significant negative coefficients for *Pinus ponderosa* at LT and *Pinus longaeva* at CB, whose reconstructed $DBH$s did not extend down to 0cm within the time frame analyzed) and near-universally negative coefficients for $DBH^2$ (exception: *Pinus longaeva* at CB).
For $\Delta AGB$, models were even more consistent, with the best models for `r round(n_spst_dAGB_DBH_best_model/ n_spst_DBH_analyzed*100)`% of species containing a positive coefficient for $DBH$ and a negative coefficient for $DBH^2$ (exception: *Pinus longaeva* at CB).

>>>>

```{r , eval=FALSE, echo=FALSE}
## Tallies for the  paragraph below (Jan12)

@@

```{r , eval=TRUE, echo=FALSE}
## Tallies for the  paragraph below (Jan6)
n_spst_DBH_analyzed= 43 # n species with DBH analyzed: 43 (45 - 2: 2 Hansley)
n_spst_RW_DBH_sig=35 #  species with sig first-order linear DBH term
n_spst_RW_DBH_2nd_order=26
n_spst_RW_DBH_2nd_order_neg=21
n_spst_BAI_DBH_best_model=42 #exception: ACRU at HF  
n_spst_BAI_DBH_best_model_pos=40 #exceptions: PIPO at LT (reconstructed DBH down to only 15cm) and PILO at CB (short DBH range on old trees), both neg but not significant
n_spst_BAI_DBH_best_model_2nd=41
n_spst_BAI_DBH_best_model_2nd_neg=40 # exception: PILO at CB
n_spst_dAGB_DBH_best_model=42 # exception: PILO at CB
```

@@

**Trends in both $BAI$ and $\Delta AGB$ were far more consistent across sites and species, most commonly increasing to a peak at intermediate $DBH$ and then declining (Fig. `r size`).**
Best models for $BAI$ included $DBH$ and $DBH^2$ for `r n_spst_BAI_DBH_best_model` of `r n_spst_DBH_analyzed` species (exception: *Acer rubrum* at HF), with a positive coefficient for $DBH$ in `r n_spst_BAI_DBH_best_model_pos` (exceptions: non-significant negative coefficients for *Pinus ponderosa* at LT and *Pinus longaeva* at CB, whose reconstructed $DBH$s did not extend down to 0cm within the time frame analyzed) and near-universally negative coefficients for $DBH^2$ (exception: *Pinus longaeva* at CB).
For $\Delta AGB$, models were even more consistent, with the best models for `r round(n_spst_dAGB_DBH_best_model/ n_spst_DBH_analyzed*100)`% of species containing a positive coefficient for $DBH$ and a negative coefficient for $DBH^2$ (exception: *Pinus longaeva* at CB).
